\cvsection{Experience}
\begin{cventries}
  \cventry
    {Senior Software Engineer}
    {Silicon Labs}
    {Copenhagen, Denmark}
    {Nov 2020 - March 2023}
    {
      \begin{cvitems}
		\item {Developed a IoT gateway SDK. A platform that connects Z-Wave, Zigbee, Bluetooth protocol stacks to specific back-ends in an unified way.}
		\item {Rust lead. Worked on transitioning the team and codebase to Rust programming language.}
		\item {Release Coordinator. End responsible in making sure releases are according quality and delivered on time to our customers.}
		\item {Unit-test expert, Consulting projects within Silicon labs on code coverage, TDD and testing related processes.}
		\item {Designed and implemented a build-system in cmake that compiles both Rust and C++ code into one library and binaries.}
		\item {Designed and implemented procedural macros that simplifies data marshalling between Rust and C code.}
		\item {Setting up Nix build and packaging system.}
      \end{cvitems}
    }
  \cventry
    {Snowdrop Programmer}
    {Massive Entertainment, a Ubisoft studio}
    {Malmö, Sweden}
    {Jan 2018 - Nov 2020}
    {
      \begin{cvitems}
		\item { Member of the snowdrop team as programmer.(C++/Visual Studio) Game engine used for Tom Clancy's The Division 2. }
        \item { Developed Asset Mover tool in snowdrop editor (C++). packing of data, dependency-tracking, asset management.}
		\item { Designed and prepared software components and tools for snowdrop. }
        \item { Developed and maintained submit assistant. perforce 3th party productivity tool(C\#). }
        \item { Supported sharpmake. C\# based solution for generating project. }
      \end{cvitems}
    }
  \cventry
    {Embedded Software Engineer}
    {Philips}
    {Eindhoven, Netherlands}
    {Feb 2016 - Jan 2018}
    {
      \begin{cvitems}
        \item {Developed Philips connectivity firmware on cypress microchips, Cortex-M4.(C++/ C, FreeRTOS, NetX).}
        \item {Implemented features related to WIFI domain: UDP, TCP/IP, HTTP, TLS, SSDP.}
        \item {Developed a Philips proprietary protocol based on SPI, UART and HTTP transports.}
        \item {Implemented a streaming protocol on top of BLE GATT profile.}
        \item {Migrated legacy C code to C++.}
        \item {Developing and maintaining test automation (C\#).}
        \item {Developing EmbeddedInfralib. a STL lookalike lib designed for embedded systems.}
        \item {Created build automation and CI tooling (Python).}
      \end{cvitems}
    }
  \cventry
    {Software Engineer}
    {TomTom Automotive (Deauville)}
    {Eindhoven, Netherlands}
    {Feb. 2013 - Jan. 2016}
    {
      \begin{cvitems}
        \item {Developed Linux based navigation software for an in-dash car system using QT framework.}
        \item{implemented GENIVI navigation services communicating over DBUS.}
        \item {Implemented tacho and gyro filters for more reliable positioning of the car. }
        \item {Lead on performance and stabilization. Profiled and improved 1.start-up behaviour, 2.performance, 3.memory usage, using profilers (valgrind) and memory leak detectors.}
        \item {Technical contact and front desk for other tier one suppliers.}
        \item {Fixed and stabilized Multithreading and mapviewer issues.}
        \item {Optimized build tooling (Bash, Cmake, Python).}
      \end{cvitems}
    }
  \cventry
    {Software Developer}
    {TomTom Automotive (MFD)}
    {Eindhoven, Netherlands}
    {Feb. 2013 - Jan. 2016}
    {
      \begin{cvitems}
        \item {part of feature team for a car multimedia system based on Android/JAVA.}
        \item {Implemented Ethernet modem support in the android platform.}
      \end{cvitems} 
    }
\end{cventries}
\newpage

\cvsection{Education}

\begin{cventries}
  \cventry
    {ICT \& Technology}
    {Fontys University of Applied Sciences}
    {Eindhoven, Netherlands}
    {Jan. 2009 - Jan. 2013}
    {
      \begin{cvitems}
        \item {Minor in embedded systems.}
      \end{cvitems}
    }
\end{cventries}
\cvsection{Courses}
\begin{cventries}
  \cventry
    {Industrial Logic}
    {Extreme Programming}
    {}
    {2016}
    {}
      \cventry
    {Topic}
    {Design Patterns}
    {}
    {2015}
    {}
      \cventry
    {Topic}
    {OO C++ Module 1,2,3}
    {}
    {2012}
    {}
\end{cventries}

